---
title: "Term paper"
subtitle: ""
author: "Rose Hörsting & Gina Reinhard"
date: "2024-09-15"
engine: knitr
bibliography: references.bib
format: 
  html:
    toc: true
    embed-resources: true
link-citations: true
csl: "apa_7th.csl"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

```{r include=FALSE}

library(checkdown)

```

#### **Chapter overview** {.unnumbered}

In this chapter, we...

```{r load-libraries, message=FALSE}

library(tidyverse)

```

## Introducing the study

@fricke2024semantic

They used the face emoji annotation system developed by @fugate2021implications.


```{r import-data, message=FALSE}

raw_data <- read_csv(file = "data/raw_data.csv")

```

## Descriptive statistics

```{r clean-data}

data <- raw_data |> 
  filter(age <= 35)

```

```{r, results=FALSE}

table(raw_data$gender)
table(raw_data$emoji_understanding)
table(raw_data$emoji_use)

```

```{r gender-count, results=FALSE}

gender_count <- data |> 
  group_by(submission_id) |> 
  count(gender)

table(gender_count$gender)

```

```{r emojiuse-count, results=FALSE}

emoji_use_count <- data |> 
  group_by(submission_id) |> 
  count(emoji_use)

table(emoji_use_count$emoji_use)

```

## Data wrangling / visualisation

### Walkthrough bar plot

Plot emoji use frequencies as barplot with ggplot:

```{r}

ggplot(emoji_use_count, mapping = aes(x = emoji_use)) + 
  geom_bar()

```

Reorder levels of factor "emoji_use":

```{r plot-emojiuse}

emoji_use_count <- emoji_use_count |> 
  mutate(emoji_use = factor(emoji_use, levels = c("nie", "selten", "gelegentlich", "oft", "in fast jeder Nachricht")))

```

Plot with ordered levels:

```{r}

ggplot(emoji_use_count, mapping = aes(x = emoji_use)) + 
  geom_bar()

```


::: callout-tip
#### Quiz time! {.unnumbered}

1\) Test question?

```{r echo=FALSE, results="asis"}

check_question("D", options = c("A", "B", "C", "D", "E"), type = "radio", 
random_answer_order = TRUE,
button_label = "Check answer", q_id = 4,
right = "Test right!",
wrong = "Test incorrect.")

```
:::

## Conclusion

## References
