---
title: "Term paper"
subtitle: ""
author: "Rose Hörsting & Gina Reinhard"
date: "2024-09-15"
engine: knitr
bibliography: references.bib
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    embed-resources: true
link-citations: true
csl: "apa_7th.csl"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

```{r include=FALSE}

library(checkdown)

```

#### **Chapter overview** {.unnumbered}

In this chapter, we...

```{r load-libraries, message=FALSE}

library(here)
library(tidyverse)

```

## Introducing the study

@fricke2024semantic

::: {.callout-note title="How did the experiment work?"}
...

They used the face emoji annotation system developed by @fugate2021implications.
Goal: Test the predictions of the pictorial approach. 

Pictorial approach @maier2023emojis vs. lexicalist approach @grosz2023semantics.

Question: Do AU differences lead to differences in meaning between the two emojis of a pair?
Hypothesis: "Small visual differences that do not correspond to AU differences ((no clear real-life counterparts)) should be semantically less relevant than visual differences that do correspond to AU differences" (4)
Method: three [AU+] and three [AU] emoji pairs, rendered in WhatsApp Android version; each emoji to occur on one pair; no emojis with symbolic components (5)

:::

```{r import-data, message=FALSE}

raw_data <- read.csv(file = here("data", "raw_data.csv"))

```

## Data wrangling

```{r clean-data}

data <- raw_data |> 
  filter(age <= 35)

```

```{r, results=FALSE}

table(raw_data$gender)
table(raw_data$emoji_understanding)
table(raw_data$emoji_use)

```

```{r gender-count, results=FALSE}

gender_count <- data |> 
  group_by(submission_id) |> 
  count(gender)

table(gender_count$gender)

```

```{r emojiuse-count, results=FALSE}

emoji_use_count <- data |> 
  group_by(submission_id) |> 
  count(emoji_use)

table(emoji_use_count$emoji_use)

```

                                   str_detect(name, "filler") ~ "filler",
                                   .default = NULL))

table(data$AU_difference)
 
```

## Data analysis/visualisation 

### Descriptive statistics

### Walkthrough bar plot

Plot emoji use frequencies as barplot with ggplot:

```{r}

ggplot(emoji_use_count, mapping = aes(x = emoji_use)) + 
  geom_bar()

```

Reorder levels of factor "emoji_use":

```{r plot-emojiuse}

emoji_use_count <- emoji_use_count |> 
  mutate(emoji_use = factor(emoji_use, levels = c("nie", "selten", "gelegentlich", "oft", "in fast jeder Nachricht")))

```

Plot with ordered levels:

```{r}

ggplot(emoji_use_count, mapping = aes(x = emoji_use)) + 
  geom_bar()

```


::: {.callout-tip}
#### Quiz time! {.unnumbered}

1\) Test question?

```{r echo=FALSE, results="asis"}

check_question("D", options = c("A", "B", "C", "D", "E"), type = "radio", 
random_answer_order = TRUE,
button_label = "Check answer", q_id = 4,
right = "Test right!",
wrong = "Test incorrect.")

```
:::

## Inserting emojis in R

😁

## Conclusion

## References
